Model_CFU

### 2017-01-05 code/HumanCdGF_cdiff_colonization.Rmd
remove IN2/DA01134 since no Day 0 CFU data

# remove samples not used or with other cdiff strains
meta_data <- 
  meta_data %>% 
  filter(Early_Euth == FALSE, cdiff_strain == 431, !cage_id == 'NP1') %>% 
  select(mouse_id, sample_id, cage_id, human_source, day, log_cfu)
shared_list_days <- meta_data %>% 
  filter(day == 0) %>% 
  select(-day, -log_cfu, -cage_id, -human_source)
shared_file <- shared_file[rownames(shared_file) %in% shared_list_days$sample_id, ]
meta_data <- filter(meta_data, !is.na(log_cfu))

@@

*** 
***
I did notice that the way I was selecting samples (Day == 0) was removing a cage, since there was no CFU recorded for Day 0. This cage is higher in CFU and does have an effect on CFU however without any CFU data for day 0 it is not completely clear there was no CDI present at day 0.

>>>>

# remove samples not used or with other cdiff strains
meta_data <- 
  meta_data %>% 
  filter(Early_Euth == FALSE, cdiff_strain == 431, !cage_id == 'NP1') %>% 
  select(mouse_id, sample_id, cage_id, human_source, day, log_cfu) %>% 
  filter(!is.na(log_cfu))
shared_list_days <- meta_data %>% 
  filter(day == 0) %>% 
  select(-day, -log_cfu, -cage_id, -human_source)
shared_file <- shared_file[rownames(shared_file) %in% shared_list_days$sample_id, ]

@@
